Code for Submission

### 2024-01-10 CodeForSubmission.Rmd
Found a typo in Fig 5 legend -- fixed

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.8, size = 2.5) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
 # geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
 # geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
 # geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "Developmental Outcome")

>>>>

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.8, size = 2.5) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
 # geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
 # geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
 # geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "Developmental Outcome")
